---
title: "fyp_unified_plot.Rmd"
author: "AndrewLampinen"
date: "July 13, 2016"
output: html_document
---

This file is for creating a plot of the overall results of the experiment, collapsed across the different experiments.

```{r}
library(rjson)
library(ggplot2)
library(tidyr)
library(dplyr)
library(lme4)
library(lmerTest)
library(stringr)
```


Exp. 1
-----------------

Read files:
```{r}
data_location = "../data/fyp_1_data/" 
files = list.files(path = data_location,pattern="data_subject_.*.json")
modular_data = vector()
polygon_data = vector()
modular_prompt_data = vector()
polygon_prompt_data = vector()
#data frame building
subject = vector()
prompt = vector()
correct_response = vector()
rt = vector()
response = vector()
response_type = vector()
condition = vector()
trial_index = vector()
score = vector()

j = 1
for (i in 1:length(files)) {
  path = paste(data_location,files[i],sep="")
  print(i)
  print(path)
  c = file(path, "r")
  l = readLines(c, -1L)
  close(c)
  these_data = lapply(X=l, fromJSON)
  if (these_data[1][[1]][[1]]$trial_type == "instructions") {
    if (length(these_data[1][[1]]) == 85 || length(these_data[1][[1]]) == 105) { #The OR checks for people who had to repeat the initial training
      this_condition = "modular"
      modular_data[length(modular_data) + 1] = these_data[1]
    }
    else {
      this_condition = "modular_prompt"
      modular_prompt_data[length(modular_prompt_data) + 1] = these_data[1]
    }
  } else {
    if (length(these_data[1][[1]]) == 85 || length(these_data[1][[1]]) == 105) { #The OR checks for people who had to repeat the initial training
     this_condition = "polygon"
     polygon_data[length(polygon_data) + 1] = these_data[1]
    }
    else {
     this_condition = "polygon_prompt"
     polygon_prompt_data[length(polygon_prompt_data) + 1] = these_data[1]
    }
  }
  
  for (trial_i in 1:length(these_data[1][[1]])) {
    if(grepl("question",gsub(" ","",these_data[1][[1]][[trial_i]]$trial_type))) {
      subject[j] = i
      condition[j] = this_condition
      prompt[j] = these_data[1][[1]][[trial_i]]$question
      correct_response[j] = these_data[1][[1]][[trial_i]]$correct_response
      response_type[j] = these_data[1][[1]][[trial_i]]$response_type
      
      response[j] = these_data[1][[1]][[trial_i]]$response
      if (gsub(' ','',response[j]) == gsub(' ','',correct_response[j])) {
        score[j] = 1
      } else {
        score[j] = 0        
      }
      rt[j] = these_data[1][[1]][[trial_i]]$rt
      trial_index[j] = trial_i
      
      j = j+1
    }
  }
}
```

data frame building
```{r}
complete_data = data.frame(subject=factor(subject),condition=condition,question=prompt,correct_response=correct_response,response=response,rt=rt,trial_index=trial_index,score=score) 

#Insert scored data
inverse_formula_scores = read.csv(paste(data_location,"inverse_formula_scored.csv",sep=""))
complete_data[inverse_formula_scores$row.names,]$score = inverse_formula_scores$score

TF_ASN_explained_scores = read.csv(paste(data_location,"TF_ASN_explained_scored.csv",sep=""))
complete_data[TF_ASN_explained_scores$row.names,]$score = TF_ASN_explained_scores$score

N9_operation_scores =read.csv(paste(data_location,"N9_operation_scored.csv",sep=""))
complete_data[N9_operation_scores$row.names,]$score = N9_operation_scores$score
N9_operation_scores[grepl("Whatis4",gsub(" ","",N9_operation_scores$question)),]$correct_response = 5
N9_operation_scores[grepl("Whatis8",gsub(" ","",N9_operation_scores$question)),]$correct_response = 3
complete_data[N9_operation_scores$row.names,]$correct_response = N9_operation_scores$correct_response #omitted because of answer explanation

N9_generator_scores = read.csv(paste(data_location,"N9_generator_scored.csv",sep=""))
complete_data[N9_generator_scores$row.names,]$score = N9_generator_scores$score

N9_inverse_scores =read.csv(paste(data_location,"N9_inverse_scored.csv",sep=""))
complete_data[N9_inverse_scores$row.names,]$score = N9_inverse_scores$score
complete_data[N9_inverse_scores$row.names,]$correct_response = 6 #omitted because of answer explanation

long_answer_scores = read.csv(paste(data_location,"long_explanations_scored.csv",sep=""))
complete_data[long_answer_scores$row.names,]$score = long_answer_scores$score

#Strict scoring -- Some questions have "partial credit" of 0.5 for almost correct answers
complete_data = complete_data %>% mutate(score_strict = floor(score)) %>% 
  mutate(polygon=grepl("polygon",condition),prompt=grepl("prompt",condition)) #Factors of condition


```

Subject Demographics

```{r}
subject_data = complete_data %>% 
  filter(grepl('education',gsub(" ","",question)) | grepl('yourgender',gsub(" ","",question)) ) %>%
  mutate(demographic_type = ifelse(grepl('education',gsub(" ","",question)),'education','gender')) %>%
  select(subject,demographic_type,response,polygon) %>%
  mutate(response = gsub(' ','',response)) %>%
  spread(demographic_type,response) %>%
  mutate(education_high = ifelse(grepl('Bachelors',education),1,ifelse(grepl('Masters',education),1,ifelse(grepl('graduate',education),1,ifelse(grepl('Doctorate',education),1,0)))))

highest_math_classes =read.csv(paste(data_location,"highest_math_class_scored.csv",sep=""))
subject_data$math_high = highest_math_classes$math_high
```


```{r}
complete_data = complete_data %>% mutate(question_type = rep(NA,nrow(complete_data))) %>% inner_join(subject_data)

#Operation questions
complete_data[grepl("Remember,toperform",gsub(" ","",complete_data$question)) & trial_index <= 20,]$question_type = 'a_operation_6' #a is so it will appear at the beginning of models as reference level, to make life easier than manually altering the contrasts
complete_data[!(grepl("identity",gsub(" ","",complete_data$question)) | grepl("inverse",gsub(" ","",complete_data$question)) | grepl("generator",gsub(" ","",complete_data$question))) & (grepl("nonagon",gsub(" ","",complete_data$question)) | grepl("+<sub>9",gsub(" ","",complete_data$question)) ),]$question_type = 'operation_9'

#Inverse Questions -- Order 6
complete_data[grepl("Remember,theinverse",gsub(" ","",complete_data$question)),]$question_type = 'inverse_nonzero_6'
complete_data[grepl("Remember,theinverse",gsub(" ","",complete_data$question)) & complete_data$correct_response == '0',]$question_type = 'inverse_zero_6'
  
#Inverse Questions -- Order 9
complete_data[grepl("Whatistheinverse",gsub(" ","",complete_data$question)) & !grepl("Remember,theinverse",gsub(" ","",complete_data$question)),]$question_type = 'inverse_nonzero_9'
#complete_data[grepl("Whatistheinverse",gsub(" ","",complete_data$question)) & !grepl("Remember,theinverse",gsub(" ","",complete_data$question)) & gsub(" ","",complete_data$correct_response) == '0',]$question_type = 'inverse_zero_9' 

#Inverse Questions -- order n
complete_data[inverse_formula_scores$row.names,]$question_type = 'inverse_formula_n'

#Generator Questions -- 6
complete_data[grepl("generatorunder",gsub(" ","",complete_data$question)) & (grepl("hexagon",gsub(" ","",complete_data$question)) | grepl("+<sub>6",gsub(" ","",complete_data$question)) ),]$question_type = 'generator_false_6'
complete_data[grepl("generatorunder",gsub(" ","",complete_data$question)) & (grepl("hexagon",gsub(" ","",complete_data$question)) | grepl("+<sub>6",gsub(" ","",complete_data$question)) ) & gsub(" ","",complete_data$correct_response) == 'Yes',]$question_type = 'generator_true_6'

#Generator Questions -- 9
complete_data[grepl("generatorunder",gsub(" ","",complete_data$question)) & (grepl("nonagon",gsub(" ","",complete_data$question)) | grepl("+<sub>9",gsub(" ","",complete_data$question)) ),]$question_type = 'generator_false_9'
complete_data[grepl("generatorunder",gsub(" ","",complete_data$question)) & (grepl("nonagon",gsub(" ","",complete_data$question)) | grepl("+<sub>9",gsub(" ","",complete_data$question)) ) & (grepl('5',gsub(" ","",complete_data$question)) | grepl('2',gsub(" ","",complete_data$question))),]$question_type = 'generator_true_9'

#Generator T/F Questions -- n
complete_data[grepl("Trueorfalse",gsub(" ","",complete_data$question)),]$question_type = 'generator_TF_n'

#Generator A/S/N Questions -- n
complete_data[grepl("always,sometimes,ornever",gsub(" ","",complete_data$question)),]$question_type = 'generator_ASN_n'
```

```{r}
model_data = complete_data %>% filter(!is.na(question_type))
model_data$question_type = factor(model_data$question_type)
```

```{r}
exp_1_data = model_data
```

Exp 2
-------------------

Read files:
```{r}
data_location = "../data/fyp_2_data/" 
files = list.files(path = data_location,pattern="data_subject_.*.json")
modular_data = vector()
polygon_data = vector()
hybrid_data = vector()
#data frame building
subject = vector()
prompt = vector()
correct_response = vector()
response_type = vector()
rt = vector()
response = vector()
condition = vector()
trial_index = vector()
score = vector()

j = 1
for (i in 1:length(files)) {
  path = paste(data_location,files[i],sep="")
  print(i)
  print(path)
  c = file(path, "r")
  l = readLines(c, -1L)
  close(c)
  these_data = lapply(X=l, fromJSON)
  if (these_data[1][[1]][[1]]$trial_type == "instructions") {
      this_condition = "modular"
      modular_data[length(modular_data) + 1] = these_data[1]
  } else {
    if (grepl("subtract",gsub(" ","",these_data[1][[1]][[1]]$instructions))) { 
        this_condition = "hybrid"
        hybrid_data[length(hybrid_data) + 1] = these_data[1]
    }
    else {
       this_condition = "polygon"
       polygon_data[length(polygon_data) + 1] = these_data[1]
    }
  }
  
  for (trial_i in 1:length(these_data[1][[1]])) {
    if(grepl("question",gsub(" ","",these_data[1][[1]][[trial_i]]$trial_type))) {
      subject[j] = i
      condition[j] = this_condition
      prompt[j] = these_data[1][[1]][[trial_i]]$question
      correct_response[j] = these_data[1][[1]][[trial_i]]$correct_response
      response_type[j] = these_data[1][[1]][[trial_i]]$response_type
      
      if (is.null(these_data[1][[1]][[trial_i]]$response)) {
        response[j] = NA
      }
      else {
        response[j] = these_data[1][[1]][[trial_i]]$response
      }
      
      if (!is.na(response[j]) && gsub(' ','',response[j]) == gsub(' ','',correct_response[j])) {
        score[j] = 1
      } else {
        score[j] = 0        
      }
      rt[j] = these_data[1][[1]][[trial_i]]$rt
      trial_index[j] = trial_i
      
      j = j+1
    }
  }
}
```

```{r}
complete_data = data.frame(subject=factor(subject),condition=condition,question=prompt,correct_response=correct_response,response=response,rt=rt,trial_index=trial_index,score=score) 

#Insert scored data
inverse_formula_scores = read.csv(paste(data_location,"inverse_formula_scored.csv",sep=""))
complete_data[inverse_formula_scores$row.names,]$score = inverse_formula_scores$score

TF_ASN_explained_scores = read.csv(paste(data_location,"TF_ASN_explained_scored.csv",sep=""))
complete_data[TF_ASN_explained_scores$row.names,]$score = TF_ASN_explained_scores$score

N9_operation_scores =read.csv(paste(data_location,"N9_operation_scored.csv",sep=""))
complete_data[N9_operation_scores$row.names,]$score = N9_operation_scores$score
N9_operation_scores[grepl("Whatis4",gsub(" ","",N9_operation_scores$question)),]$correct_response = 5
N9_operation_scores[grepl("Whatis8",gsub(" ","",N9_operation_scores$question)),]$correct_response = 3
complete_data[N9_operation_scores$row.names,]$correct_response = N9_operation_scores$correct_response #omitted because of answer explanation

N9_generator_scores = read.csv(paste(data_location,"N9_generator_scored.csv",sep=""))
complete_data[N9_generator_scores$row.names,]$score = N9_generator_scores$score

N9_inverse_scores =read.csv(paste(data_location,"N9_inverse_scored.csv",sep=""))
complete_data[N9_inverse_scores$row.names,]$score = N9_inverse_scores$score
complete_data[N9_inverse_scores$row.names,]$correct_response = 6 #omitted because of answer explanation

long_answer_scores = read.csv(paste(data_location,"long_explanations_scored.csv",sep=""))
complete_data[long_answer_scores$row.names,]$score = long_answer_scores$score

#Strict scoring -- Some questions have "partial credit" of 0.5 for almost correct answers
complete_data = complete_data %>% mutate(score_strict = floor(score)) %>% 
  mutate(polygon=grepl("polygon",condition),prompt=grepl("prompt",condition)) #Factors of condition


```

Subject Demographics

```{r}
subject_data = complete_data %>% 
  filter(grepl('education',gsub(" ","",question)) | grepl('yourgender',gsub(" ","",question)) ) %>%
  mutate(demographic_type = ifelse(grepl('education',gsub(" ","",question)),'education','gender')) %>%
  select(subject,demographic_type,response,polygon) %>%
  mutate(response = gsub(' ','',response)) %>%
  spread(demographic_type,response) %>%
  mutate(education_high = ifelse(grepl('Bachelors',education),1,ifelse(grepl('Masters',education),1,ifelse(grepl('graduate',education),1,ifelse(grepl('Doctorate',education),1,0)))))

highest_math_classes = read.csv(paste(data_location,"highest_math_class_scored.csv",sep=""))
subject_data$math_high = highest_math_classes$math_high
```

Exclude subjects who responded 4 or higher on familiarity with modular arithmetic or mathematical groups: they know too much

```{r}
complete_unfiltered_data = complete_data
subjects_to_exclude = unique(complete_data[grepl("Howfamiliarareyou",gsub(" ","",complete_data$question)) & (grepl("4",complete_data$response) | grepl("5",complete_data$response)),]$subject)

complete_data = complete_unfiltered_data %>% filter(!(subject %in% subjects_to_exclude))

table(complete_unfiltered_data[(complete_unfiltered_data$subject %in% subjects_to_exclude) & complete_unfiltered_data$trial_index == 3,]$condition)
```



Exclude subjects who responded 4 or higher on familiarity with modular arithmetic or mathematical groups: they know too much

```{r}
complete_unfiltered_data = complete_data
subjects_to_exclude = unique(complete_data[grepl("Howfamiliarareyou",gsub(" ","",complete_data$question)) & (grepl("4",complete_data$response) | grepl("5",complete_data$response)),]$subject)

complete_data = complete_unfiltered_data %>% filter(!(subject %in% subjects_to_exclude))


```


```{r}
complete_data = complete_data %>% mutate(question_type = rep(NA,nrow(complete_data))) %>% inner_join(subject_data)

#Operation questions
complete_data[grepl("Remember,toperform",gsub(" ","",complete_data$question)),]$question_type = 'a_operation_6' #a is so it will appear at the beginning of models as reference level, to make life easier than manually altering the contrasts
complete_data[!(grepl("identity",gsub(" ","",complete_data$question)) | grepl("inverse",gsub(" ","",complete_data$question)) | grepl("generator",gsub(" ","",complete_data$question))) & (grepl("nonagon",gsub(" ","",complete_data$question)) | grepl("+<sub>9",gsub(" ","",complete_data$question)) ),]$question_type = 'operation_9'

#Inverse Questions -- Order 6
complete_data[grepl("Remember,theinverse",gsub(" ","",complete_data$question)),]$question_type = 'inverse_nonzero_6'
complete_data[grepl("Remember,theinverse",gsub(" ","",complete_data$question)) & complete_data$correct_response == '0',]$question_type = 'inverse_zero_6'
  
#Inverse Questions -- Order 9
complete_data[grepl("Whatistheinverse",gsub(" ","",complete_data$question)) & !grepl("Remember,theinverse",gsub(" ","",complete_data$question)),]$question_type = 'inverse_nonzero_9'
complete_data[grepl("Whatistheinverse",gsub(" ","",complete_data$question)) & !grepl("Remember,theinverse",gsub(" ","",complete_data$question)) & gsub(" ","",complete_data$correct_response) == '0',]$question_type = 'inverse_zero_9' 

#Inverse Questions -- order n
complete_data[inverse_formula_scores$row.names,]$question_type = 'inverse_formula_n'

#Generator Questions -- 6
complete_data[grepl("generatorunder",gsub(" ","",complete_data$question)) & (grepl("hexagon",gsub(" ","",complete_data$question)) | grepl("+<sub>6",gsub(" ","",complete_data$question)) ),]$question_type = 'generator_false_6'
complete_data[grepl("generatorunder",gsub(" ","",complete_data$question)) & (grepl("hexagon",gsub(" ","",complete_data$question)) | grepl("+<sub>6",gsub(" ","",complete_data$question)) ) & gsub(" ","",complete_data$correct_response) == 'Yes',]$question_type = 'generator_true_6'

#Generator Questions -- 9
complete_data[grepl("generatorunder",gsub(" ","",complete_data$question)) & (grepl("nonagon",gsub(" ","",complete_data$question)) | grepl("+<sub>9",gsub(" ","",complete_data$question)) ),]$question_type = 'generator_false_9'
complete_data[grepl("generatorunder",gsub(" ","",complete_data$question)) & (grepl("nonagon",gsub(" ","",complete_data$question)) | grepl("+<sub>9",gsub(" ","",complete_data$question)) ) & (grepl('5',gsub(" ","",complete_data$question)) | grepl('2',gsub(" ","",complete_data$question))),]$question_type = 'generator_true_9'

#Generator T/F Questions -- n
complete_data[grepl("Trueorfalse",gsub(" ","",complete_data$question)),]$question_type = 'generator_TF_n'

#Generator A/S/N Questions -- n
complete_data[grepl("always,sometimes,ornever",gsub(" ","",complete_data$question)),]$question_type = 'generator_ASN_n'
```

```{r}
model_data = complete_data %>% filter(!is.na(question_type))
model_data$question_type = factor(model_data$question_type)
```

```{r}
exp_2_data = model_data
```

Exp. 3
-----------

Read files:
```{r}
data_location = "../data/fyp_3_data/" 
files = list.files(path = data_location,pattern="data_subject_.*.json")
modular_data = vector()
polygon_data = vector()
hybrid_data = vector()
#data frame building
subject = vector()
prompt = vector()
explain = vector()
explanation = vector()
correct_response = vector()
rt = vector()
response = vector()
response_type = vector()
condition = vector()
trial_index = vector()
score = vector()
used_diagram = vector()

j = 1
for (i in 1:length(files)) {
  path = paste(data_location,files[i],sep="")
  print(i)
  print(path)
  c = file(path, "r")
  l = readLines(c, -1L)
  close(c)
  these_data = lapply(X=l, fromJSON)
  if (these_data[1][[1]][[1]]$trial_type == "instructions") {
      this_condition = "modular"
      modular_data[length(modular_data) + 1] = these_data[1]
  } else {
    if (grepl("subtract",gsub(" ","",these_data[1][[1]][[1]]$instructions))) { 
        this_condition = "hybrid"
        hybrid_data[length(hybrid_data) + 1] = these_data[1]
    }
    else {
       this_condition = "polygon"
       polygon_data[length(polygon_data) + 1] = these_data[1]
    }
  }
  
  for (trial_i in 1:length(these_data[1][[1]])) {
    if(grepl("question",gsub(" ","",these_data[1][[1]][[trial_i]]$trial_type))) {
      subject[j] = i
      condition[j] = this_condition
      prompt[j] = these_data[1][[1]][[trial_i]]$question
      correct_response[j] = these_data[1][[1]][[trial_i]]$correct_response
      explain[j] = these_data[1][[1]][[trial_i]]$explain
      response_type[j] = these_data[1][[1]][[trial_i]]$response_type
      if (is.null(these_data[1][[1]][[trial_i]]$explanation) | is.list(these_data[1][[1]][[trial_i]]$explanation)) { #is.list handles the unfortunate partial matching of explanation to explanation_history when explanation is null
        explanation[j] = NA
      } else {
        explanation[j] = these_data[1][[1]][[trial_i]]$explanation
      }
      
      if (is.null(these_data[1][[1]][[trial_i]]$response)) {
        response[j] = NA
      }
      else {
        response[j] = these_data[1][[1]][[trial_i]]$response
      }
      
      if (!is.null(these_data[1][[1]][[trial_i]]$orientation_history) && is.list(these_data[1][[1]][[trial_i]]$orientation_history) ) {
        used_diagram[j] = length(these_data[1][[1]][[trial_i]]$orientation_history) > 2
      } else {
        used_diagram[j] = NA
      }
      
      if (!is.na(response[j]) && gsub(' ','',response[j]) == gsub(' ','',correct_response[j])) {
        score[j] = 1
      } else {
        score[j] = 0        
      }
      rt[j] = these_data[1][[1]][[trial_i]]$rt
      trial_index[j] = trial_i
      
      j = j+1
    }
  }
}
```


```{r}
complete_data = data.frame(subject=factor(subject),condition=condition,question=prompt,correct_response=correct_response,response=response,rt=rt,trial_index=trial_index,score=score,response_type=response_type) 
# #n-1,n-x
# write.table(complete_data[grepl("formula",gsub(" ","",complete_data$question)),c(1,4,5,8,10)],paste(data_location,"inverse_formula_to_score.csv",sep=''),sep=",")

# #Highest math class completed, 1 if algebra 2/trig/stats or higher, 0 else
# write.table(complete_data[grepl('mathclass',gsub(' ','',complete_data$question)),c(1,4,5,8,10)],paste(data_location,"highest_math_class_to_score.csv",sep=''),sep=",")

#NOT YET SCORED for explanations
# #n=9 operation questions
# write.table(complete_data[(grepl("Whatis8",gsub(" ","",complete_data$question)) | grepl("Whatis4",gsub(" ","",complete_data$question)))& grepl("explaininwords",gsub(" ","",complete_data$question)) ,c(1,3,4,5,7)],paste(data_location,"N9_operation_to_score.csv",sep=''),sep=",")
# 
# #n=9 generator questions
# write.table(complete_data[grepl("generatorunder",gsub(" ","",complete_data$question)) & (grepl("nonagon",gsub(" ","",complete_data$question)) | grepl("+<sub>9",gsub(" ","",complete_data$question)) ),c(1,3,4,5,7)],paste(data_location,"N9_generator_to_score.csv",sep=''),sep=",")
# 
# #n=9 inverse with explanations
# write.table(complete_data[grepl("inverseof3",gsub(" ","",complete_data$question)) & (grepl("nonagon",gsub(" ","",complete_data$question)) | grepl("+<sub>9",gsub(" ","",complete_data$question)) ),c(1,4,5,7)],paste(data_location,"N9_inverse_to_score.csv",sep=''),sep=",")
# 
# #generator T/F and A/S/N with explanations
# write.table(complete_data[grepl("explaininwords",gsub(" ","",complete_data$question)) & (grepl("Trueorfalse",gsub(" ","",complete_data$question)) | grepl("always,sometimes,ornever",gsub(" ","",complete_data$question))),c(1,4,5,7)],paste(data_location,"TF_ASN_explained_to_score.csv",sep=''),sep=",")

#DONE
#Long responses to check if correct:
#write.table(complete_data[(nchar(levels(complete_data$response)[complete_data$response]) > nchar(levels(complete_data$correct_response)[complete_data$correct_response])) & !(grepl('multi',gsub(' ','',complete_data$response_type)) | grepl("explaininwords",gsub(" ","",complete_data$question)) | grepl("formula",gsub(" ","",complete_data$question)) | (grepl('Whatisyour|languages|mathclass|Doyou|Didyou|Howfamiliar|Pleasedescribe',gsub(' ','',complete_data$question)))),c('subject','question','correct_response','response','score')],'long_explanations_to_score.csv',sep=',')

```

```{r}
complete_data = data.frame(subject=factor(subject),condition=condition,question=prompt,correct_response=correct_response,response=response,rt=rt,explain=explain,explanation=explanation,trial_index=trial_index,score=score,used_diagram=used_diagram) 

#Insert scored data
inverse_formula_scores = read.csv(paste(data_location,"inverse_formula_scored.csv",sep=""))
complete_data[inverse_formula_scores$row.names,]$score = inverse_formula_scores$score

long_answer_scores = read.csv(paste(data_location,"long_explanations_scored.csv",sep=""))
complete_data[long_answer_scores$row.names,]$score = long_answer_scores$score

#Strict scoring -- Some questions have "partial credit" of 0.5 for almost correct answers
complete_data = complete_data %>% mutate(score_strict = floor(score)) %>% 
  mutate(polygon=grepl("polygon",condition)) #Factors of condition


```




Change dummy coding to compare hybrid and polygon to modular.
```{r}
contrasts(complete_data$condition) = cbind(c(0,0,1),c(1,0,0))
colnames(contrasts(complete_data$condition)) = c('polygon','hybrid')
contrasts(complete_data$condition) 
```


```{r}
subject_data = complete_data %>% 
  filter(grepl('education',gsub(" ","",question)) | grepl('yourgender',gsub(" ","",question)) ) %>%
  mutate(demographic_type = ifelse(grepl('education',gsub(" ","",question)),'education','gender')) %>%
  select(subject,demographic_type,response,polygon) %>%
  mutate(response = gsub(' ','',response)) %>%
  spread(demographic_type,response) %>%
  mutate(education_high = ifelse(grepl('Bachelors',education),1,ifelse(grepl('Masters',education),1,ifelse(grepl('graduate',education),1,ifelse(grepl('Doctorate',education),1,0)))))

highest_math_classes =read.csv(paste(data_location,"highest_math_class_scored.csv",sep=""))
subject_data$math_high = highest_math_classes$math_high
```

Exclude subjects who responded 4 or higher on familiarity with modular arithmetic or mathematical groups: they know too much

```{r}
complete_unfiltered_data = complete_data
subjects_to_exclude = unique(complete_data[grepl("Howfamiliarareyou",gsub(" ","",complete_data$question)) & (grepl("4",complete_data$response) | grepl("5",complete_data$response)),]$subject)

complete_data = complete_unfiltered_data %>% filter(!(subject %in% subjects_to_exclude))


```

That's a lot of exclusions


```{r}
complete_data = complete_data %>% mutate(question_type = rep(NA,nrow(complete_data))) %>% inner_join(subject_data)

#Operation questions
complete_data[grepl("Remember,toperform",gsub(" ","",complete_data$question)),]$question_type = 'a_operation_6' #a is so it will appear at the beginning of models as reference level, to make life easier than manually altering the contrasts
complete_data[!(grepl("identity",gsub(" ","",complete_data$question)) | grepl("inverse",gsub(" ","",complete_data$question)) | grepl("generator",gsub(" ","",complete_data$question))) & (grepl("nonagon",gsub(" ","",complete_data$question)) | grepl("+<sub>9",gsub(" ","",complete_data$question)) ),]$question_type = 'operation_9'

#Inverse Questions -- Order 6
complete_data[grepl("Remember,theinverse",gsub(" ","",complete_data$question)),]$question_type = 'inverse_nonzero_6'
complete_data[grepl("Remember,theinverse",gsub(" ","",complete_data$question)) & gsub(' ','',complete_data$correct_response) == '0',]$question_type = 'inverse_zero_6'

  
#Inverse Questions -- Order 9
complete_data[grepl("Whatistheinverse",gsub(" ","",complete_data$question)) & !grepl("Remember,theinverse",gsub(" ","",complete_data$question)),]$question_type = 'inverse_nonzero_9'
complete_data[grepl("Whatistheinverse",gsub(" ","",complete_data$question)) & !grepl("Remember,theinverse",gsub(" ","",complete_data$question)) & gsub(" ","",complete_data$correct_response) == '0',]$question_type = 'inverse_zero_9' 

#Inverse Questions -- order n
complete_data[inverse_formula_scores$row.names,]$question_type = 'inverse_formula_n'

#Generator Questions -- 6
complete_data[grepl("generatorunder",gsub(" ","",complete_data$question)) & (grepl("hexagon",gsub(" ","",complete_data$question)) | grepl("+<sub>6",gsub(" ","",complete_data$question)) ),]$question_type = 'generator_false_6'
complete_data[grepl("generatorunder",gsub(" ","",complete_data$question)) & (grepl("hexagon",gsub(" ","",complete_data$question)) | grepl("+<sub>6",gsub(" ","",complete_data$question)) ) & gsub(" ","",complete_data$correct_response) == 'Yes',]$question_type = 'generator_true_6'

#Generator Questions -- 9
complete_data[grepl("generatorunder",gsub(" ","",complete_data$question)) & (grepl("nonagon",gsub(" ","",complete_data$question)) | grepl("+<sub>9",gsub(" ","",complete_data$question)) ),]$question_type = 'generator_false_9'
complete_data[grepl("generatorunder",gsub(" ","",complete_data$question)) & (grepl("nonagon",gsub(" ","",complete_data$question)) | grepl("+<sub>9",gsub(" ","",complete_data$question)) ) & (grepl('5',gsub(" ","",complete_data$question)) | grepl('2',gsub(" ","",complete_data$question))),]$question_type = 'generator_true_9'

#Generator T/F Questions -- n
complete_data[grepl("Trueorfalse",gsub(" ","",complete_data$question)),]$question_type = 'generator_TF_n'

#Generator A/S/N Questions -- n
complete_data[grepl("always,sometimes,ornever",gsub(" ","",complete_data$question)),]$question_type = 'generator_ASN_n'
```

```{r}
model_data = complete_data %>% filter(!is.na(question_type))
model_data$question_type = factor(model_data$question_type)
```

```{r}
model_data$condition = relevel(model_data$condition,ref='modular') #Because the previous doesn't seem to carry over
```

```{r}
exp_3_data = model_data
```


Unified plot
----------------------

```{r}
sem <- function(x) {sd(x, na.rm=TRUE) / sqrt(length(x))}
```

```{r}
exp_1_data = exp_1_data %>% mutate(condition = ifelse(polygon,'polygon','modular')) %>% select(subject,condition,question_type,score_strict,math_high) %>% mutate(subject = factor(paste('1-',subject,sep=''))) 
exp_2_data = exp_2_data %>% select(subject,condition,question_type,score_strict,math_high) %>% mutate(subject = factor(paste('2-',subject,sep=''))) 
exp_3_data = exp_3_data %>% select(subject,condition,question_type,score_strict,math_high) %>% mutate(subject = factor(paste('3-',subject,sep=''))) 
```

```{r}
#full_data = rbind(exp_1_data,exp_2_data,exp_3_data)
full_data = rbind(exp_2_data,exp_3_data) #Remove experiment 1 data per Jay's suggestion
#Various fixes
qtypes = levels(full_data$question_type)
qtypes[1] = 'operation_6' #Rename to make consolidation easier
levels(full_data$question_type) = qtypes
full_data$condition = factor(full_data$condition,c('polygon','modular','hybrid'))
```

```{r}
plotting_data = full_data %>% 
  mutate(aggregated_question_type = substr(levels(question_type)[question_type],1,nchar(levels(question_type)[question_type])-2)) %>%
  group_by(subject,condition,aggregated_question_type) %>%
  summarize(percent_correct = mean(score_strict)) %>% 
  group_by(condition,aggregated_question_type) %>%
  summarize(percent_correct.mean = mean(percent_correct),percent_correct.sem = sem(percent_correct)) %>%
  filter(!is.na(condition))

plotting_data$aggregated_question_type = factor(plotting_data$aggregated_question_type)
plotting_data$aggregated_question_type = factor(plotting_data$aggregated_question_type,levels(plotting_data$aggregated_question_type)[c(8,6,7,4,2,5,3,1)])

plotting_data = plotting_data %>% 
  mutate(main_result = aggregated_question_type %in% c('generator_true','inverse_zero','inverse_nonzero'))
```

```{r}
ggplot(data=plotting_data,aes(aggregated_question_type,percent_correct.mean,fill=condition,alpha=main_result)) + 
  geom_bar(stat="identity",position="dodge") +
  geom_errorbar(aes(ymax=percent_correct.mean+percent_correct.sem,ymin=percent_correct.mean-percent_correct.sem,width=0.5),position=position_dodge(width=0.9)) +
  scale_x_discrete(breaks=levels(plotting_data$aggregated_question_type),
                      labels=c("Operation", "Inverse of Non-zero", "Inverse of Zero", "Identifying Gen.", "Identifying Non-gen.", "Inverse Formula", "Generator T/F", "Generator A/S/N")) +  
  scale_fill_manual(values = c("#00BFC4", "#F8766D", "#FFCC33")) +
  scale_alpha_manual(values= c(0.33,1.0))+
  annotate("text",x=1.86,y=1.0,label='*',alpha=0.5,size=8)+ #Stars mark those where 95% CI in the meta analysis combined across orders does not overlap zero
  annotate("text",x=2.15,y=1.0,label='*',alpha=0.5,size=8)+
  annotate("text",x=2.86,y=1.0,label='*',alpha=0.5,size=8)+
  annotate("text",x=3.15,y=1.0,label='*',alpha=0.5,size=8)+
  annotate("text",x=3.86,y=1.0,label='*',alpha=0.5,size=8)+
  annotate("text",x=4.15,y=1.0,label='*',alpha=0.5,size=8)+
  labs(y = 'Mean % Correct', x= 'Question Type') + 
  guides(alpha=FALSE)+
  ggtitle("Overall Results") + 
  theme_bw(base_size=20)+
  theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.text.x=element_text(angle=45,hjust=1))
```



